The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2016-08-24 article.tex
Worked on the SDG section

  Many of the rendering options are available as parameters in the core API
  and as methods on the DepictionGenerator class. This includes substructure
  coloring, exemplified with this example reaction (see Fig.~2\ref{fig:depiction}):

@@

@@

  \subsection*{Figure 6 - Dependencies between CDK modules.}\label{fig:deps}
      Visualization of the dependencies between CDK modules. For example,
      the cdk-core depends on the cdk-interfaces module. A few higher level
      modules have been left out: cdk-builder3dtools, cdk-legacy, and
      cdk-depict.

>>>>

  Many of the rendering options are available as parameters in the core API
  and as methods on the DepictionGenerator class. This includes substructure
  coloring, exemplified with this example reaction (see Fig.~\ref{fig:depiction}):

@@

\begin{verbatim}
StructureDiagramGenerator sdg = new StructureDiagramGenerator();
sdg.setMolecule(someMolecule);
sdg.generateCoordinates();
IAtomContainer layedOutMol = sdg.getMolecule();
\end{verbatim}

The API has hardly changed. The internals, however, have significantly. Besides
the aforementioned overlap resolution, the engine also handles large ring
systems much better, using a honeycomb layout approach~\cite{FIXME}, % FIXME
and handles stereochemistry of the input. Previously, double bond stereochemistry
was supported, but the new engine more efficiently uses this when creating 2D
layouts. Furthermore, the engine assigns wedge bond information based on
tetrahedral stereochemistry. These features are exemplified by the following
code and the resulting layout depiction in Figure~\ref{fig:sdgstereo}.

\begin{verbatim}
someMolecule = fromSMILES.....
sdg.setMolecule(someMolecule);
sdg.generateCoordinates();
IAtomContainer layedOutMol = sdg.getMolecule();
\end{verbatim}

% FIXME: complete code example

@@

\subsection*{Figure 6 - Structure diagram generation for structures with
double bond and tetrahedral stereochemistry.}\label{fig:sdgstereo}

\includegraphics[width=\textwidth]{sdg2.png}

  \subsection*{Figure 7 - Dependencies between CDK modules.}\label{fig:deps}
      Visualization of the dependencies between CDK modules. For example,
      the cdk-core depends on the cdk-interfaces module. A few higher level
      modules have been left out: cdk-builder3dtools, cdk-legacy, and
      cdk-depict.
